My title\thanks{Code and data are available at: LINK.}

### 2024-02-08 paper/paper.qmd
not sure
added black cherry tree graph

library(tidyverse)
library(palmerpenguins)
install.packages(tinytex)
library(tinytex)
```

@@

>>>>

library(tidyverse)
library(palmerpenguins)
```

@@

We are interested in the height of 31 black cherry trees (@fig-blackcherrytrees)
```{r}
#| label: fig-blackcherrytrees
#| fig-cap: Height of 31 Black Cherry Trees
#| echo: false

datasets::trees |> 
  as_tibble() |> 
  ggplot(aes(y = Height)) +
  geom_bar() +
  labs(x = "Number of Black Cherry Trees", y = "Height (ft)") + 
  theme_bw()

```

### 2024-02-08 paper/paper.tex
added black cherry tree graph

\begin{document}
\maketitle
\begin{abstract}
First sentence. Second sentence. Third sentence. Fourth sentence.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, borderline west={3pt}{0pt}{shadecolor}, enhanced, frame hidden, breakable, interior hidden, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

\begin{verbatim}
geom_point: na.rm = FALSE
stat_identity: na.rm = FALSE
position_identity 
\end{verbatim}

@@

>>>>

\begin{document}
\maketitle
\begin{abstract}
First sentence. Second sentence. Third sentence. Fourth sentence.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, enhanced, boxrule=0pt, interior hidden, sharp corners, frame hidden, breakable]}{\end{tcolorbox}}\fi

@@

@@

We are interested in the height of 31 black cherry trees
(Figure~\ref{fig-blackcherrytrees})

{\centering \includegraphics{paper_files/figure-pdf/fig-blackcherrytrees-1.pdf}

\caption{\label{fig-blackcherrytrees}Height of 31 Black Cherry Trees}
